Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-03-27 why.tex
Reorganize so it builds. New Figure 1

\item{\textit{Interdisciplinary research}: Intensive, time-bounded collaborative events are an excellent opportunity to experiment with concepts, questions, and methods that span boundaries within and across disciplines. Despite the fact that such interdisciplinary experiments are highly impactful \cite{Hall2012-hi}, they are often discouraged in risk averse traditional academia \cite{Sung2003-go, Rhoten2004-fk}}.

@@

It is worth noting that the reasons for participants to attend a hack week are as diverse as the reasons for running such an event.
Beginner participants may attend primarily to learn a new technique, while others may attend to gain experience in mentoring, or to focusing on an existing project already in progress (for more details on setting objectives, see supplementary materials).

>>>>

\item{\textit{Interdisciplinary research}: Intensive, time-bounded collaborative events are an excellent opportunity to experiment with concepts, questions, and methods that span boundaries within and across disciplines. Despite the fact that interdisciplinary experiments are impactful \cite{Hall2012-hi}, they are often discouraged in risk averse traditional academia \cite{Sung2003-go}}.

@@

\noindent It is worth noting that the reasons for participants to attend a hack week are as diverse as the reasons for running such an event.
Beginner participants may attend primarily to learn a new technique, while others may attend to gain experience in mentoring, or to focusing on an existing project already in progress (for more details on setting objectives, see supplementary materials).
